Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, and the WEAI Conference}

### 2023-02-27 latex/paper/Spillover.tex
Remove "online" appendix reference

Last, in Section \ref{sec:event_study}, I extend estimation of treatment and spillover effects into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}. This allows for a very common setting in which treatment turns on for different units in different periods. Their proposed two-stage estimator first estimates group and time fixed-effects using untreated/not-yet-treated observations. Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed-effects. Then these estimated unit and time fixed-effects are subtracted from the observed outcome \emph{in the full sample}. The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects. In the online appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.

>>>>

Last, in Section \ref{sec:event_study}, I extend estimation of treatment and spillover effects into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}. This allows for a very common setting in which treatment turns on for different units in different periods. Their proposed two-stage estimator first estimates group and time fixed-effects using untreated/not-yet-treated observations. Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed-effects. Then these estimated unit and time fixed-effects are subtracted from the observed outcome \emph{in the full sample}. The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects. In the appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.
